%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,7pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jayanta Pandit} \\ \vspace{1pt}
    \small \href{mailto:jayantapandit@outlook.in}{\underline{jayantapandit@outlook.in}} $|$ 
    \href{https://linkedin.com/in/panditjay}{\underline{linkedin.com/in/panditjay}} $|$
    \href{https://github.com/jayzsh}{\underline{github.com/jayzsh}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Asansol Engineering College, West Bengal}{Asansol, West Bengal}
      {Bachelor of Technology in Electronics and Communication Engg.}{Sept. 2021 -- Jun. 2025}
        \resumeItemListStart
            \resumeItem{Cumulative GPA: 9.47}
            \resumeItem{Relevant Coursework: Data Structures and Algorithms, Programming Methodologies, Digital Systems and Circuit Design, Microprocessors, Computer Networks, Cryptography, Statistics}
            \resumeItem{Leadership: GirlScript Foundation - Asansol Chapter}
        \resumeItemListEnd
    \resumeSubheading
      {DAV Model School, Durgapur}{Durgapur, WB}
      {Higher Secondary (AISSCE, E-PCM-CS, Score: 95.0\%)}{Apr. 2018 -- Mar. 2020}
    \resumeSubheading
      {De Nobili School, Maithon}{Maithon, Jharkhand}
      {Secondary (ICSE, Score: 94.0\%)}{Apr. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Freelance Web Engineer \& IT Consultant}{Mar. 2023 -- Present}
      {Trinity.sh Consulting}{Remote, Asansol, WB}
      \resumeItemListStart
        \resumeItem{Serving contract as a \textbf{React \& Node.js developer for Manjeet Kaur Foundation}; \textbf{managing CI/CD pipelines and deployment processes} for their back-end infrastructure}
        \resumeItem{Serving contract as a \textbf{Python Automation Engineer} for GrowXP, New Delhi; \textbf{building and maintaining Newsletter dispatch automation, SEO Tracking }and\textbf{ WhatsApp Business marketing tools}}
      \resumeItemListEnd

 \resumeSubheading
      {MVP Development Lead}{Nov. 2022 -- Mar. 2023}
      {SmallTownTalks}{Remote, Asansol, WB}
      \resumeItemListStart
        \resumeItem{Designed and built \textbf{NextJS Web UI} for company's \textbf{Google Maps, OpenWeatherMaps \& Geolocation API} based \textbf{SaaS stealth product}}
        \resumeItem{Served Contract as a  Full Stack Engineer for The Dhobi Ghat start-up and built their \textbf{Order placing Native Android App} (published on Play Store),\textbf{ Order management employee dashboard and CMS} (React.js) and\textbf{ Order delivery Android App} (for employees and admin boards)}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Freelance Full Stack Web Developer}{May. 2022 -- Nov. 2022}
      {Prachar More}{Remote, Asansol, WB}
      \resumeItemListStart
        \resumeItem{Served contract as full stack web developer for\textbf{ Franchise Hub}, India \& Uttarakhand based adventure sports and travel company \textbf{The Himalayan Exploration}}
        \resumeItem{Helped entrepreneurs amplify their online influence and engagement through targeted SEO efforts, and planned web page content delivery}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ACORN Lexical Database for English} $|$ \emph{C99, C++17, Qt5, CMake}}{Jan. 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Wrote a lightning-fast \textbf{database query C++ library }for Princeton's WordNet 3 database (155,000+ definitions)}
            \resumeItem{Used\textbf{ Qt5 GUI toolkit for building Native desktop front-end} for Debian and derivatives}
            \resumeItem{Used a \textbf{modified binary search implementation to quickly parse, retrieve and compile database items} for the command-line or GUI front-end}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{TurboZAS -- Text-based Zombie Apocalypse Arcade for Console} $|$ \emph{Turbo C++, BGI-GL}}{Nov. 2018 -- Mar. 2020}
          \resumeItemListStart
            \resumeItem{Zombie Apocalypse Survivor (shortened, ZAS) is a 16-bit \textbf{retro style escape-room} adventure game on the Windows 3.x \textbf{DOSBox} terminal built with the TurboC/C++ compiler (1992); features original classic SFX}
            \resumeItem{Uses 16-bit BGI graphics library to render graphical elements in the terminal}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{URLTag -- Tag Analytics API for the Web} $|$ \emph{TypeScript, Python, Node.js, Express, MongoDB}}{Mar. 2023}
          \resumeItemListStart
            \resumeItem{Used to \textbf{generate unique tracking URLs} (that responds with a pixel payload) and \textbf{monitor hit count from each}}
            \resumeItem{URLTag uses \textbf{GET-image HTTP requests} to notify the API when a HTML render is due}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, Kotlin, SQL, JavaScript (TypeScript), Bash, Java} \\
     \textbf{Web}{: Next.js, React, Node.js, Express, Socket.io, Strapi CMS, HTML/CSS, Material UI, Tailwind CSS, Figma} \\
    \textbf{Mobile}{: Android Native (Android SDK w/ Java \& Kotlin)} \\
   \textbf{Desktop}{: Qt5 Native} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, Hostinger, Heroku, Vim, VSCode, PyCharm, IntelliJ, Jira, Slack} \\
     \textbf{Databases}{: MongoDB, PostgreSQL} \\
    }}
 \end{itemize}

 \section{Awards \& Achievements}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{
    \item {
\resumeItemListStart
\resumeItem{Deemed \textbf{Top Contributor (Top 15th)} in IIIT Kalyani’s Winter of Code 2.0 (2021-22) Open-Source event among 1500+ participants}
\resumeItem{Qualified Level 3 of the Google’s Foobar Challenge (2021)}
\resumeItem{Achieved state \textbf{rank 8086 in WBJEE 2020-21}}
\resumeItem{\textbf{Valedictorian} — De Nobili School, Maithon, 2018; \textbf{ranked 2nd} in Institute among 80+ candidates in ICSE 2017-18}
\resumeItem{Bagged Award of Excellence with\textbf{ 1st rank at School Level, 7th rank at Zonal Level} in SOF’s Cyber Olympiad 2017}
}}
 \end{itemize}


%-------------------------------------------
\end{document}
